\textit{Urban and building multiscale co-simulation: case study implementations on two university campuses}

### 2016-12-20 coverletter/CoverLetter.tex
Paper submission

The attached manuscript entitled “Urban and building multiscale co-simulation: case study implementations on two university campuses” is an original research article that I would like to submit for consideration in Journal of Building Performance Simulation. This paper outlines the process of co-simulation between EnergyPlus and CitySim for two campuses. This paper builds upon the work from two previous conference papers and includes properly-referenced content from both papers. References of those papers are found below: \\[12pt]
Thomas, D., Miller, C., Kämpf, J., Schlueter, A., 2014. Multiscale co-simulation of EnergyPlus and CitySim models derived from a building information model, in: Proceedings of Bausim 2014: Fifth German-Austrian IBPSA Conference. Presented at the Bausim 2014: Fifth German-Austrian IBPSA Conference, IBPSA, Aachen, Germany, pp. 469–476. doi:10.13140/2.1.4639.1040\\[12pt]

@@

Any questions or comments can be directed to myself as the corresponding author. I am avail-
able via email at miller.clayton@arch.ethz.ch and by phone at 1-402-403-0090.

>>>>

The attached manuscript entitled “Urban and building multiscale co-simulation: case study implementations on two university campuses” is an original research article that I would like to submit for consideration in the Journal of Building Performance Simulation. This paper outlines the process of co-simulation between EnergyPlus and CitySim for two campuses. This paper builds upon the work from two previous conference papers and includes properly-referenced content from both papers. References of those papers are found below: \\[12pt]
Thomas, D., Miller, C., Kämpf, J., Schlueter, A., 2014. Multiscale co-simulation of EnergyPlus and CitySim models derived from a building information model, in: Proceedings of Bausim 2014: Fifth German-Austrian IBPSA Conference. Presented at the Bausim 2014: Fifth German-Austrian IBPSA Conference, IBPSA, Aachen, Germany, pp. 469–476. doi:10.13140/2.1.4639.1040\\[12pt]

@@

Any questions or comments can be directed to myself as the corresponding author. I am available via email at miller.clayton@arch.ethz.ch and by phone at 1-402-403-0090.

### 2016-12-20 initialsubmission/UMEM_CoSim_Anonymous.tex
Paper submission

\author{Clayton Miller\textsuperscript{a}%
$^{\ast}$\thanks{$^\ast$Corresponding author. Email: miller.clayton@arch.ethz.ch}, 
Daren Thomas\textsuperscript{a},
J\'er\^ome K\"ampf\textsuperscript{b},
and Arno Schlueter\textsuperscript{a}\\
\vspace{6pt}
\textsuperscript{a}{\em Architecture and Building Systems (A/S), Institute of Technology in Architecture (ITA), ETH Z\"urich, Z\"urich, Switzerland};\\
\textsuperscript{b}{\em Solar Energy and Building Physics Laboratory (LESO-PB), Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Lausanne, Switzerland}
\received{Submission for review on April 30, 2016} %TARGETED!
}

>>>>

% \author{Clayton Miller\textsuperscript{a}%
% $^{\ast}$\thanks{$^\ast$Corresponding author. Email: miller.clayton@arch.ethz.ch}, 
% Daren Thomas\textsuperscript{a},
% J\'er\^ome K\"ampf\textsuperscript{b},
% and Arno Schlueter\textsuperscript{a}\\
% \vspace{6pt}
% \textsuperscript{a}{\em Architecture and Building Systems (A/S), Institute of Technology in Architecture (ITA), ETH Z\"urich, Z\"urich, Switzerland};\\
% \textsuperscript{b}{\em Solar Energy and Building Physics Laboratory (LESO-PB), Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Lausanne, Switzerland}
% \received{Submission for review on April 30, 2016} %TARGETED!
% }
